Hybrid platforms and bargaining power

### 2023-03-25 src/paper/application.tex
Add more graphs

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \begin{tikzpicture}[scale=0.8]
            \centering
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
                    xtick={0, 1}, ytick={0}, extra y ticks={1}, extra y tick style={yticklabel={$f(1)$}},
                    xlabel={$s$}]
                \addplot[name path=f, blue,ultra thick] {x^2};
                \node[anchor= east] at (axis cs: .9, .9^2) {$f(N_P, sN_F)$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);

@@

                \node[anchor=north west] at (axis cs: .1, .9) {Fringe ($A$)};
                \node[anchor=south east] at (axis cs: .9, .1) {Player $P$};
            \end{axis}
        \end{tikzpicture}
        \caption{Fringe firms are complements}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
                xtick={0, 1}, ytick={0}, extra y ticks={1}, extra y tick style={yticklabel={$f(1)$}},
                xlabel={$s$}]
                \addplot[name path=f, blue,ultra thick] {x^0.5};
                \node[anchor=north west] at (axis cs: .6, .6^0.5) {$\tilde{f}(N_P, sN_F)$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);

@@

                \node[anchor=north west] at (axis cs: .1, .9) {Fringe ($A$)};
                \node[anchor=south east] at (axis cs: .9, .1) {Player $P$};
            \end{axis}
        \end{tikzpicture}
        \caption{Fringe firms are substitutes}
    \end{subfigure}
    \caption{Distribution of value between the platform and the fringe (with $w(s) \equiv 1$)}
    \label{fig:outcome_based_bargaining_power}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \caption{Illustration of \cref{prop:share_of_platform}}
    \label{fig:increase_N_P_platform}
\end{figure}

@@

Finally, let us conclude this section by establishing a stronger result for a more restrictive class of profit functions.
In the following, I assume that the profit function has a specific, additive form.
Intuitively, this means that -- in terms of total profits generated -- the platform's and the fringe firms' products are substitutable to each other according to some constant ratio.\footnote{
    Note that it does not mean that their products are \emph{substitutes} in the usual, demand theory sense.
    They still might be complements to each other.
}
\begin{proposition}
    \label{prop:aggregate_size_additive}
    Let $f$ have the following, additive form:
    \begin{align*}
        f(N_P, N_F) = g(\alpha N_P + \beta N_F)
    \end{align*}
    where $\alpha, \beta > 0$.
    Furthermore, assume that $g$ is twice differentiable and that $g'' < 0$.
    Then
    \begin{align*}
        \frac{\partial N_F^*}{\partial N_P} < -\frac{\alpha}{\beta}.
    \end{align*}
\end{proposition}
As opposed to the previous results, this proposition tells us something about the total profits generated by the platform and the fringe firms as a function of the platform's product variety, and under equilibrium entry behavior by the fringe firms.
In particular, it states that total profits increase if the total profit function is convex (products are substitutes), and decreases otherwise.
This result has particularly strong implications in models where total profits (or total product variety) has a monotone relationship with consumer welfare, such as those in \textcite{anderson2020aggregative}.
\Cref{sec:example} also presents a model in which this is the case.

>>>>

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \begin{tikzpicture}[scale=0.8]
            \centering
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
                    xtick={0, 1}, ytick={0}, xlabel={$s$}]
                \addplot[name path=f, blue,ultra thick] {x^2};
                \node[anchor= east] at (axis cs: .9, .9^2) {$f(N_P, sN_F)$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);

@@

                \node[anchor=north west] at (axis cs: .1, .9) {Fringe ($A$)};
                \node[anchor=south east] at (axis cs: .9, .1) {Platform ($P$)};
            \end{axis}
        \end{tikzpicture}
        \caption{Fringe firms are complements}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
                xtick={0, 1}, ytick={0}, xlabel={$s$}]
                \addplot[name path=f, blue,ultra thick] {x^0.5};
                \node[anchor=north west] at (axis cs: .6, .6^0.5) {$\tilde{f}(N_P, sN_F)$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);

@@

                \node[anchor=north west] at (axis cs: .1, .9) {Fringe ($A$)};
                \node[anchor=south east] at (axis cs: .9, .1) {Platform ($P$)};
            \end{axis}
        \end{tikzpicture}
        \caption{Fringe firms are substitutes}
    \end{subfigure}
    \caption{Distribution of value between the platform and the fringe (with $w(s) \equiv 1$)}
    \label{fig:outcome_based_bargaining_power}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
                xtick={0, 1}, ytick={0}, axis lines=left, xlabel={$s$}]
                \addplot[name path=f, blue,ultra thick] {ln(1+x)};
                \addplot[name path=tildef, dashed, black] {x};
                \node[anchor=north west] at (axis cs: .6, 0.5) {$f(N_P, sN_F)$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \draw[name path=top] (axis cs:0,0.693) -- (axis cs:1,0.693);
                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,0.693);

                \node[anchor=north west] at (axis cs: .05, .65) {Fringe ($A$)};
                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
            \end{axis}
        \end{tikzpicture}
        \caption{Profit shares with $f$}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
                xtick={0, 1}, ytick={0}, axis lines=left, xlabel={$s$}]
                \addplot[name path=f, dashed, black] {ln(1+x)};
                \addplot[name path=tildef, blue,ultra thick] {x};
                \node[anchor=south east] at (axis cs: 0.6, 0.6) {$\tilde{f}(N_P, sN_F)$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \draw[name path=top] (axis cs:0,1) -- (axis cs:1,1);
                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1);

                \addplot [fill=blue, fill opacity=0.05] fill between [of=tildef and bottom];
                \addplot [fill=red, fill opacity=0.05] fill between [of=tildef and top];

                \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($A$)};
                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
            \end{axis}
        \end{tikzpicture}
        \caption{Profit shares with $\tilde{f}$}
    \end{subfigure}
    \caption{Illustration of \cref{prop:share_of_platform}}
    \label{fig:increase_N_P_platform}
\end{figure}

@@

        \draw[name path=piF,domain=0.01:5.5,variable=\x,blue,ultra thick] plot ({\x},{8*((\x)/(0.3+\x))-8*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
        \draw[name path=piF2,domain=0.01:5.5,variable=\x,blue,ultra thick] plot ({\x},{6*((\x)/(0.3+\x))-6*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
        \draw[name path=IF,domain=0.01:5.5,variable=\x,red,ultra thick] plot ({\x},{(\x)/3});

        \node[anchor=south] at (5,1) {$\pi_F(N_P, n_F)$};
        \node[anchor=north] at (5,0.6) {$\pi_F(N_P', n_F)$};
        \node[anchor=south east] at (5,5/3) {$I_F n_F$};

        \fill [name intersections={of=piF and IF, name=i, total=\t}]
            [black] (i-2) circle (1pt);
        \draw[dashed] (i-2) -- (i-2 |- 0,0) node[below] {$N_F^*$};
        \fill [name intersections={of=piF2 and IF, name=i2, total=\t}]
            [black] (i2-2) circle (1pt);
        \draw[dashed] (i2-2) -- (i2-2 |- 0,0) node[below] {$N_F^{*'}$};

        \draw[->] (i-2 |- 0,0.5) -- (i2-2 |- 0,0.5);
    \end{tikzpicture}
    \caption{Comparative statistics for equilibrium entry (fringe are substitutes)}
    \label{fig:comparative_N_F}
\end{figure}

Finally, let us conclude this section by establishing a stronger result for a more restrictive class of profit functions.
In the following, I assume that the profit function has a specific, additive form.
Intuitively, this means that -- in terms of total profits generated -- the platform's and the fringe firms' products are substitutable to each other according to some constant ratio.\footnote{
    Note that it does not mean that their products are substitutes in the usual, demand theory sense.
    They still might be complements to each other.
}
\begin{proposition}
    \label{prop:aggregate_size_additive}
    Let $f$ have the following, additive form:
    \begin{align*}
        f(N_P, N_F) = g(\alpha N_P + \beta N_F)
    \end{align*}
    where $\alpha, \beta > 0$.
    Furthermore, assume that $g$ is twice differentiable and that $g'' < 0$.
    Then
    \begin{align*}
        \frac{\partial N_F^*}{\partial N_P} < -\frac{\alpha}{\beta}.
    \end{align*}
\end{proposition}
As opposed to the previous results, this proposition tells us something about the total profits generated by the platform and the fringe firms as a function of the platform's product variety, and under equilibrium entry behavior by the fringe firms.
In particular, it states that total profits increase if the total profit function is convex (products are substitutes), and decreases otherwise.
This result has particularly strong implications in models where total profits (or total product variety) has a monotone relationship with consumer welfare, such as those in \textcite{anderson2020aggregative}.
\Cref{sec:example} also presents a model in which this is the case.
